Hydras \& Co.

### 2022-03-03 doc/part-hydras.tex
add compatibility notes (Gaia) (up to page 85)
add compatibility notes (Gaia)

@@

@@

>>>>

\paragraph{\gaiacompat}
In \gaia, the boolean functions associated with limit and successor ordinals are called \texttt{T1limit} and \texttt{T1is\_succ}.

\inputsnippets{HydraGaia_Examples/Demob}

@@

\begin{exercise}[\gaia]
  Look for the \gaia-theorem which corresponds to \texttt{succb\_iff}.
\end{exercise}

\subsubsection{Successor function on \texttt{E0}}

@@

\paragraph{\gaiacompat}
In \gaia, addition and multiplication of ordinal terms below $\epsilon_0$ are respectively called \texttt{T1add} and \texttt{T1mul}. Please refer to Sect.~\ref{sect:plus-mult-gaia-hydras} about compatibility of both arithmetics.
